MWA tied-array processing III: Microsecond time resolution via a synthesis filter

### 2019-10-23 ipfb.tex
Changed wording for clarity

It is well known that scaling a function in the time domain produces the inverse scaling in the Fourier domain.
This fact motivates an alternative strategy for mitigating spectral leakage.
Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response function that is similar in shape, but $P$ times narrower than the original analysis filter.
A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.
In this way, spectral leakage can be contained arbitrarily close to the ``correct'' channel by choosing a sufficiently high value of $P$.

>>>>

It is well known that scaling a function in the time domain produces the inverse scaling in the Fourier domain.
This fact motivates an alternative strategy for mitigating spectral leakage.
Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response that is similar in shape, but $P$ times narrower than the frequency response of the original analysis filter.
A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.
In this way, spectral leakage can be contained arbitrarily close to the ``correct'' channel by choosing a sufficiently high value of $P$.
